\section*{Question 7}

Suppose there are three special dice, A, B, C which have the following numbers on their six faces: \\
A:\@ 1,1,6,6,8,8\\
B:\@ 2,2,4,4,9,9\\
C:\@ 3,3,5,5,7,7\\
The dice are fair in the sense that each of the faces have the same probability of coming up.
(i). Suppose we roll dice A and B.
What is the probability that the number that comes up on A is less than the one that comes up on B?
(ii) Suppose your friend, with whom you go out for dinner often, offers you the following.
At the end of each dinner, you can choose any one of the three dice.
She/He would then choose one of the two dice that are remaining.
Then both of you roll your respective dice.
Whoever gets the smaller number would pay for the dinner.
Would you take the offer?

\subsection*{Solution}

\subsubsection*{(i)}

Let \( P(A < B) \) denote the probability that the number that comes up on A is less than the one that comes up on B.
Then, we have
\begin{align*}
    P (A < B)
     & =
    \frac{2}{6} \times \Big( \frac{6}{6} + \frac{2}{6} + \frac{2}{6} \Big)
    =
    \frac{2}{6} \times \frac{10}{6}
    =
    \frac{20}{36}
    =
    \boxed{ \frac{5}{9} }
    >
    \frac{1}{2}
\end{align*}

\subsubsection*{(ii)}

Similarly, we have
\begin{align*}
    P (B < C)
     & =
    \frac{2}{6} \times \Big( \frac{4}{6} + \frac{4}{6} + \frac{2}{6} \Big)
    =
    \frac{2}{6} \times \frac{10}{6}
    =
    \frac{20}{36}
    =
    \frac{5}{9}
    >
    \frac{1}{2}
    \\
    P (C < A)
     & =
    \frac{2}{6} \times \Big( \frac{6}{6} + \frac{4}{6} + \frac{0}{6} \Big)
    =
    \frac{2}{6} \times \frac{10}{6}
    =
    \frac{20}{36}
    =
    \frac{5}{9}
    >
    \frac{1}{2}
\end{align*}

Thereby, picking any of the dice, there is a winning strategy for the friend, since they can pick up one of the other dice so that they can avoid paying.
It is better to \underline{not take the offer}.
