\section*{Question 2}

Suppose we have two boxes and \( 2 d \) balls, of which \( d \) are black and \( d \) are red.
Initially \( d \) of the balls are placed in box-1 and the remaining in box-2.
At each instant \( n, n=1,2, \cdots \), a ball is chosen at random from each box and the two balls are placed in the opposite boxes.
Let \( X_{0} \) denote number of black balls initially in box-1 and let \( X_{n} \) denote number of black balls in box-1 after the exchange at \( n \), \( n=1,2, \cdots \).
Argue that \( \left \{ X_{n}\right \} \) is a Markov chain.
Find the transition probabilities of the Markov chain \( \left \{ X_{n}\right \} \).
State which are transient states and which are recurrent states.
Is the chain irreducible?

\subsection*{Solution}

Let \( X_{n} \) denote the number of black balls in box-1 after the exchange at \( n \), \( n=1,2, \dots \).
The state space is \( S=\left \{0,1,2, \dots , d\right \} \).
The number of black balls in either of the boxes, of either of the colors, only depends on \( X_{n} \) and not on the history of the process.
Hence, \( \left \{ X_{n}\right \} \) is a Markov chain.

The transition probabilities are given by
\[
    p_{xy}=\operatorname{Prob}\left[X_{n+1}=y \mid X_{n}=x\right]
\]
where \( x,y \in S \), and can be computed as
\[
    p_{xy}=
    \begin{cases}
        \frac{x}{d} \frac{x}{d}
         & \text{if } y = x-1
        \\
        \frac{x}{d} \frac{d-x}{d} + \frac{d-x}{d} \frac{x}{d}
         & \text{if } y = x
        \\
        \frac{d-x}{d} \frac{d-x}{d}
         & \text{if } y = x + 1
    \end{cases}
\]
And we can see that the sum over all \( y \) for a given \( x \) is 1, as expected.

The chain is irreducible and all the states are recurrent.
